---
# format: typst
format: qmd_ctutypst_letter-typst
recipient: "`r params$contact`"
address_recipient: false
address_recipient_line1: "`r params$sponsor`"
address_recipient_line2: ""
address_recipient_line3: ""
address_recipient_line4: ""
address_recipient_line5: ""
space_after_recipient: 20pt
subject: "Cost estimate for DCR services"
subject2: ""
sender: "Dr. Ueli Reber"
sender_title: "Head of Business Operations"
sender_line1: "DCR"
sender_line2: "sitem"
sender_line3: "Freiburgstrasse 3"
sender_line4: "3010 Bern"
sender_line5: "Switzerland"
sender_line6: "www.dcr.unibe.ch"
department: "Department of Clinical Research"
faculty: "Faculty of Medicine"
includesenderright: false
signoff: false
keep-md: true
keep-typ: true
params:
  studyname: "Some Long, Ominous, Probably PithY, title"
  acronym: "SLOPPY"
  projnum: 1234
  consultingnum: 5678
  sponsor: "Sponsor"
  contact: "Dr McDoctorson"
  design: "Randomized-controlled trial"
  intervention: "IMP/IMD/..."
  n_participants: 100
  n_sites: 1
  location: "Swiss"
  conduct_time: 5
  complex: "simple"
  cturep: "CTU employee"
  # workpackages: NULL
  internal: FALSE
  total: NULL
  discount: NULL
  expenses: NULL
  notes: NA
  break_ftes: FALSE
  break_totals: FALSE
  break_notes: FALSE
  break_tasks: NULL
  break_projinfo: FALSE
  first_page_text: "template text"
  initcosting: TRUE
  include_design: TRUE
  include_int: TRUE
  include_participants: TRUE
  filename: "filename"
  vat: FALSE
execute: 
  echo: false
  warning: false
  message: false
---

```{=typst}
#v(-8pt)
#set table(stroke: 0pt)
#text(size: 8pt)[
```

```{r}
#| results: asis
if(!params$initcosting){
  cat("**Amendment to an existing service agreement**\n\n")
}
```

```{=typst}
#v(-5pt)
```

```{r}
#| results: asis
cat(paste0("**Project: ", params$studyname, " (", params$acronym, ")**\n\n"))
```

```{=typst}
#v(-5pt)
```

```{r}
#| results: asis
cat(paste0("**DCR internal ", ifelse(params$initcosting, "consulting", "project"), " number: ", ifelse(params$initcosting, params$consultingnum, params$projnum), "**"))
```

```{=typst}
]
```

Dear `r params$contact`,


`r params$first_page_text`

For questions regarding this offer, please contact your DCR consultant or send an email to [operations.dcr\@unibe.ch](mailto:operations.dcr@unibe.ch){.email}.

We look forward to your reply.

`#linebreak() `{=typst}

Kind regards,
`#linebreak() `{=typst}
`#linebreak() `{=typst}
Dr. Ueli Reber
`#linebreak() `{=typst}
Head of Business Operations

```{r}
#| label: genprojinfo
#| results: asis
#| eval: !expr params$break_projinfo
cat(knitr::raw_block("#pagebreak()", type = "typst"))
```

### General project information {.unnumbered}

Project name and acronym: **`r paste0(params$studyname, " (", params$acronym, ")")`**

Institution: **`r params$sponsor`**

Responsible: **`r params$contact`**

```{r}
#| eval: !expr params$include_design
#| results: asis
#| echo: false
cat(paste0('Study design: **', params$design, "**\n\n"))
```

```{r}
#| eval: !expr params$include_int
#| results: asis
#| echo: false
cat(paste0('Type of intervention: **', params$intervention, "**\n\n"))
```

```{r, eval = params$include_participants, results='asis', echo = FALSE}
#| eval: !expr params$include_participants
#| results: asis
#| echo: false
cat(paste0('Number of participants: **', params$n_participants, "** from **", 
    params$n_sites, " ", params$location, "** site(s) over a study time of **", 
    params$conduct_time, "** years."))
```




```{r}
#| label: pkg_funs

breaks_tf <- n_breaks <- FALSE

library(gt)
library(CTUCosting)
library(dplyr)
library(glue)
gt_fn <- function(x){
  gt::gt(x) |> 
    gt::tab_options(table.font.size = "8pt",
                    table.width = "100%",
                    row_group.background.color = "lightgrey",
                    data_row.padding = "2pt",
                    table.font.names = "Arial",
                    table.font.color = "black",
                    table.font.color.light = "black",
                    # # Remove all main table borders
                    # table.border.top.width = px(10),
                    # table.border.bottom.width = px(10),
                    # # Remove column label borders
                    # column_labels.border.bottom.width = px(0),
                    # # Remove body borders
                    # table_body.border.top.width = px(0),
                    # table_body.border.bottom.width = px(0), 
                    # # Removes the vertical borders for the overall table frame
                    # table.border.left.style = "hidden",
                    # table.border.right.style = "hidden",
                    # # Removes vertical borders between columns
                    # table_body.hlines.style = "hidden", # Horizontal lines
                    # table_body.vlines.style = "hidden",  # Vertical lines
                    column_labels.border.bottom.width = px(0),
                    table_body.border.bottom.width = px(0),
                    table_body.border.top.width = px(0)
    ) |> 
    cols_align(columns = `Cost (CHF)`,
               align = "right") |> 
    tab_style(
      style = cell_text(v_align = "top"),
      locations = cells_body()
    ) |> 
    tab_style(
      style = cell_text(v_align = "top"),
      locations = cells_column_labels(columns = everything())
    )
}

gt_widths <- function(x){
  x  |> 
    gt::cols_width(Task ~ "20%",
                   Description ~ "60%",
                   Hours ~ "7%",
                   `Cost (CHF)` ~ "13%",
    )
}
fte_gt_widths <- function(x){
  x  |> 
    gt::cols_width(Description ~ "60%",
                   FTE ~ "12%",
                   `Number of years` ~ "15%",
                   `Cost (CHF)` ~ "13%",
    )
}

ftedata <- readRDS("ftedata")
workpackagedata <- readRDS("workpackagedata")
```


```{r}
#| label: taskstitle
#| results: asis
if(nrow(workpackagedata) > 0){
  cat("### Tasks for DCR to provide {.unnumbered}")
}
```

```{r}
#| label: tasks
if(nrow(workpackagedata) > 0){
  tmp <- workpackagedata  |>
    select_for_pdf() |>
    group_by(Service) |>
    mutate(Cost = format(Cost, big.mark = "'", nsmall = 0)) |>
    rename(`Cost (CHF)` = Cost)
}
breaks <- as.numeric(params$break_tasks)
n_breaks <- length(breaks)
breaks_tf <- n_breaks > 0 
nobreaks <- !breaks_tf
```

```{r}
#| label: tasksout
if(nobreaks & nrow(workpackagedata) > 0){
  tmp %>%
    gt_fn() |>
    gt_widths()
} 
```

```{r}
#| label: tasksloop
#| results: asis
if(breaks_tf & nrow(workpackagedata) > 0){
  ends <- c(breaks, nrow(tmp))
  starts <- c(1, breaks + 1)
  
  res <- lapply(seq_along(starts),
                \(x) {
                  knitr::knit_child(text = c("```{r, echo = FALSE, message = FALSE}",
                                             glue("index <- (starts[{x}]):(ends[{x}])"),
                                             "  tmp[index ,] |> ",
                                             "  gt_fn() |> gt_widths()",
                                             "```"),
                                    quiet = TRUE)
                })
  
  for(i in seq_along(res)){
    cat(res[[i]])
    
    if(i < length(res)) cat(knitr::raw_block("#pagebreak()", type = "typst"))
  }
}
```

```{r}
#| label: breakftes
#| results: asis
#| eval: !expr params$break_ftes
knitr::raw_block("#pagebreak()", type = "typst")
```

```{r}
#| label: ftes_title
#| eval: !expr ftedata$fte
#| results: asis
cat("### Full time equivalents {.unnumbered}\n\n")

# cat(paste0("Position title: **", params$fte$role, "**"))
```

```{r}
#| label: ftes
#| eval: !expr ftedata$fte
ftedata$costs |> 
  # as.data.frame() |> 
  rename(Description = desc,
         FTE = prop,
         `Number of years` = units,
         Cost = cost) |>
  mutate(Cost = format(Cost, big.mark = "'", nsmall = 0)) |>
  rename(`Cost (CHF)` = Cost) |> 
  group_by(fte_role) |> 
  gt_fn() |> 
  tab_style(style = cell_text(align = "right"),
            locations = cells_column_labels(columns = c("FTE", `Number of years`, `Cost (CHF)`))) |> 
  fte_gt_widths()
```




```{r}
#| labels: expenseslab
#| results: asis
if(!is.null(params$expenses)){
  cat("### Expenses {.unnumbered}")
}
```


```{r}
#| labels: expensestab
if(!is.null(params$expenses)){
  params$expenses |> 
    as.data.frame() |> 
    rename(`Cost (CHF)` = Cost..CHF.) |> 
    mutate(`Cost (CHF)` = format(`Cost (CHF)`, big.mark = "'", nsmall = 0)) |>
    gt_fn() |> 
    gt::cols_width(Division ~ "28%",
                   Description ~ "60%",
                   `Cost (CHF)` ~ "12%")
}
```

```{r}
#| label: breaktotals
#| results: asis
#| eval: !expr params$break_totals
knitr::raw_block("#pagebreak()", type = "typst")
```

### Totals {.unnumbered}

```{r}
#| label: totalstab
if(!is.null(params$total)){
  params$total |> 
    as.data.frame() |> 
    rename(`Cost (CHF)` = Cost..CHF.) |> 
    gt_fn() |> 
    gt::cols_width(Description ~ "87%",
                   `Cost (CHF)` ~ "13%",
    )
}
```

```{r breaknotes}
#| eval: !expr params$break_notes
knitr::raw_block("#pagebreak()", type = "typst")
```

```{r}
#| label: notes
#| results: asis
notes <- params$notes
if(length(notes) > 0 && !is.na(notes) && notes != "NA"){
  cat("### Notes: {.unnumbered}\n\n")
  cat(notes)
  cat("\n\n")
}
```


### General notes: {.unnumbered}

- This cost estimate is valid for **two months** from the date of issue.

- The estimated effort and associated costs may vary depending on the complexity and specific requirements of the project.

- All costs mentioned above are rounded up to the nearest 1 CHF.

```{r}
#| results: asis
if(params$vat) cat("- The cost estimate does **not** include VAT (8.1%) which may apply.\n\n")

if(any(grepl("Discount due to number of hours", params$total$Description))) 
  cat("The discount is calculated from eligible work packages and might not be based on the overall amount.\n\n")

```

- The hourly rate used for this cost estimate is subject to **annual review and adjustment**. Please refer to [www.dcr.unibe.ch](https://www.dcr.unibe.ch) for the current hourly rates.

- If you have any questions regarding this cost estimate, please contact your DCR consultant or [operations.dcr@unibe.ch](mailto:operations.dcr@unibe.ch){.email}.

